### 2017-11-07 submission/manuscript.Rmd
small fix

Our analysis found a continuous decrease in Shannon diversity from control to adenoma to carcinoma and a significantly increased relative risk for carcinoma with this lower diversity. Using only the CRC associated genera this relative risk was higher than what was observed for Shannon diversity. However, by using the full community instead of only the CRC associated genera the AUC of the classification models increased. Although we analyze a data set with a large number of total individuals each individual study was underpowered for effect size differences of 10% or below between the case and control.

>>>>

Our analysis found a continuous decrease in Shannon diversity from control to adenoma to carcinoma and a significantly increased relative risk for carcinoma with this lower diversity. Using only the CRC associated genera this relative risk was higher than what was observed for Shannon diversity. However, by using the full community instead of only the CRC associated genera the AUC of the classification models increased. Although we analyze a data set with a large number of total individuals each individual study was underpowered for effect size differences of 10% or below between the case and control group.

### 2017-11-07 submission/manuscript.tex
small fix

Our analysis found a continuous decrease in Shannon diversity from
control to adenoma to carcinoma and a significantly increased relative
risk for carcinoma with this lower diversity. Using only the CRC
associated genera this relative risk was higher than what was observed
for Shannon diversity. However, by using the full community instead of
only the CRC associated genera the AUC of the classification models
increased. Although we analyze a data set with a large number of total
individuals each individual study was underpowered for effect size
differences of 10\% or below between the case and control.

>>>>

Our analysis found a continuous decrease in Shannon diversity from
control to adenoma to carcinoma and a significantly increased relative
risk for carcinoma with this lower diversity. Using only the CRC
associated genera this relative risk was higher than what was observed
for Shannon diversity. However, by using the full community instead of
only the CRC associated genera the AUC of the classification models
increased. Although we analyze a data set with a large number of total
individuals each individual study was underpowered for effect size
differences of 10\% or below between the case and control group.
